Theoretical evaluation of the potential advantages of cloud IDEs for research and didactic

### 2019-06-21 che.tex
Changed title

\begin{document}
%%% Mehrere Autoren werden durch \and voneinander getrennt.
%%% Die Fußnote enthält die Adresse sowie eine E-Mail-Adresse.
%%% Das optionale Argument (sofern angegeben) wird für die Kopfzeile verwendet.
\title[Eclipse Che for Education]{Eclipse Che for Fair and Easy Education}
%%%\subtitle{Untertitel / Subtitle} % falls benötigt
\author[Leonhard Applis]
{Leonhard Applis \footnote{Technische Hochschule Georg Simon Ohm, \email{Leonhard.Applis@Protonmail.com}}}
%\startpage{-} % Beginn der Seitenzählung für diesen Beitrag
\editor{Gesellschaft für Informatik}    % Namen der Herausgeber
\booktitle{SKILL 2019} % Name des Tagungsband
%\band{Lecture Note in Informatics (LNI) – Seminars, Gesellschaft für Informatik, Bonn 2019}
\year{2019}
%%%\lnidoi{18.18420/provided-by-editor-02} % Falls bekannt
\maketitle

@@

\subsection{Vulnerability}
The last problem is the vulnerability to malevolent users. 
Someone who already is in possession of a valid account can drain the shared resources of a full cluster, therefore blocking  any  other  user  from  work.
This  can  also  be achieved by human error. 
It is therefore important to not only restrict access to project resources, but also the double-check and guard the releases.

Some security risks can also emerge from docker-images as well \cite{PE13} but are out of scope for this paper.

\section{Benefits for Education}
\label{sec:EvalEdu}
In addition to the previous mentioned benefits, there are more points about Che that are especially important for educational purposes, such as courses in the university, professional school or research departments.
For simplicity only universities will be addressed.
\subsection{New motivational and intuitive Courses}
Eclipse Che provides the possibility to learn primary cloud-technologies hands on and in a simple and supportive manner. 
Unfortunately, these topics are currently not widely teached at university.
Che makes it possible to teach students fundamentals of modern software development.
Depending on the courses subject, one can either provide scalable software or a running environment. 
With suitable material provided, it's easy to learn cloud native development, DevOps or Cloud-Operations. 
Even complicated topics, such as micro-services and IoT-applications can easily be adapted inside Che \cite{IV18} and performed as for example as group-projects with a common goal. 
The student will need to understand cloud-components as well as team-work to succeed with Che.

>>>>

\begin{document}
\title[theoretical evaluation of the potential advantages of cloud IDEs for research and didactic]{Theoretical evaluation of the potential advantages of cloud IDEs for research and didactic}
\subtitle{on the example of Eclipse Che} % falls benötigt
\author[Leonhard Applis]
{Leonhard Applis \footnote{Technische Hochschule Georg Simon Ohm, \email{Leonhard.Applis@Protonmail.com}}}
%\startpage{-} % Beginn der Seitenzählung für diesen Beitrag
\editor{Gesellschaft für Informatik}    % Namen der Herausgeber
\booktitle{SKILL 2019} % Name des Tagungsband
%\band{Lecture Note in Informatics (LNI) – Seminars, Gesellschaft für Informatik, Bonn 2019}
\year{2019}
%%%\lnidoi{18.18420/provided-by-editor-02} % Falls bekannt
\maketitle

@@

\subsection{Vulnerability}
The last problem is the vulnerability to malevolent users. 
Someone who already is in possession of a valid account can drain the shared resources of a full cluster, therefore blocking  any  other  user  from  work.
This  can  also  be achieved by human error. 
It is therefore important to not only restrict access to project resources, but also the double-check and guard the releases.
\section{Benefits for Education}
\label{sec:EvalEdu}
In addition to the previous mentioned benefits, there are more points about Che that are especially important for educational purposes, such as courses in the university, professional school or research departments.
For simplicity only universities will be addressed.
\subsection{New motivational and intuitive Courses}
Eclipse Che provides the possibility to learn primary cloud-technologies hands on and in a simple and supportive manner. 
Che makes it possible to teach students fundamentals of modern software development.
Depending on the courses subject, one can either provide scalable software or a running environment. 
With suitable material provided, it's easy to learn cloud native development, DevOps or Cloud-Operations. 
Even complicated topics, such as micro-services and IoT-applications can easily be adapted inside Che \cite{IV18} and performed as for example as group-projects with a common goal. 
The student will need to understand cloud-components as well as team-work to succeed with Che.
